Locally Conservative Discontinuous Petrov-Galerkin Finite Elements for Fluid Problems

### 2013-11-22 docs/Truman/LocalConservation/paper/paper.tex
Added coarse stokes cylinder results to lc paper

\paragraph{Inf Sup in Kernel Condition} is satisfied automatically due to the use of optimal
test functions. First of all, we characterize the ``kernel'' space:
\begin{equation}
\begin{array}{rl}
\bfU_0  := & \{ \bfw \in \bfU \, : \, c(q,\bfw) = 0 \quad \forall q \in Q\} \\[8pt]
 = &\{ (u,\bfsig,\hat{u},\hat{t}) \, : \, \langle \hat{t},1_K \rangle = 0
 \quad \forall K \}
\end{array}
\end{equation}
In other words, the kernel space contains only the equilibriated fluxes.
With $\bfu \in \bfU_0$, we have then:
\begin{equation}
   \sup_{\bfw \in \bfU_0} \frac{| a(\bfu,\bfw) |}{|| \bfw ||_{\bfU} }
 \geq \frac{| b(\bfu,T \bfu) |}{|| \bfu ||}
= \sup_{(v,\bftau)}
\frac{| b((u,\bfsig,\hat{u},\hat{t}), (v,\bftau)) |}{|| (v,\bftau) ||}
\geq \gamma^2 || (u,\bfsig,\hat{u},\hat{t}) ||
\end{equation}
where $\gamma$ is the stability constant for the standard continuous DPG formulation.

@@

\begin{figure}[p]
\centering
\begin{subfigure}[t]{0.5\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/StokesCylinder/umag6_NC6.png}
\caption{Nonconservative with $r=0.6$}
\label{fig:stokesCylinderNC6}
\end{subfigure}
\begin{subfigure}[t]{0.5\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/StokesCylinder/umag6_C6.png}
\caption{Conservative with $r=0.6$}
\label{fig:stokesCylinderC6}
\end{subfigure}
\begin{subfigure}[t]{0.5\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/StokesCylinder/umag9_NC6.png}
\caption{Nonconservative with $r=0.9$}
\label{fig:stokesCylinderNC9}
\end{subfigure}
\begin{subfigure}[t]{0.5\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/StokesCylinder/umag9_C6.png}
\caption{Conservative with $r=0.9$}
\label{fig:stokesCylinderC9}
\end{subfigure}
\caption{Stokes flow around a cylinder after 6 refinement steps - velocity magnitude}
\label{fig:stokesCylinder9}
\end{figure}

>>>>

\paragraph{Inf Sup in Kernel Condition} is satisfied automatically due to the use of optimal
test functions. First of all, we characterize the ``kernel'' space:
\begin{equation}
\begin{array}{rl}
\bfU_0  := & \{ \bfw \in \bfU \, : \, c(q,\bfw) = 0 \quad \forall q \in Q\} \\[8pt]
 = &\{ (u,\bfsig,\hat{u},\hat{t}) \, : \, \langle \hat{t},1_K \rangle = 0
 \quad \forall K \}
\end{array}
\end{equation}
In other words, the kernel space contains only the equilibriated fluxes.
With $\bfu \in \bfU_0$, we have then:
\begin{equation}
   \sup_{\bfw \in \bfU_0} \frac{| a(\bfu,\bfw) |}{|| \bfw ||_{\bfU} }
   \geq \frac{| b(\bfu,T \bfu) |}{|| \bfu ||}
   = \frac{| b(\bfu,T \bfu) |}{|| T\bfu ||}\frac{||T\bfu||}{||\bfu||}
   = \sup_{(v,\bftau)}\frac{| b((u,\bfsig,\hat{u},\hat{t}), (v,\bftau)) |}{|| (v,\bftau) ||}
   \frac{||T\bfu||}{||\bfu||}
   \geq \gamma^2 || (u,\bfsig,\hat{u},\hat{t}) ||
\end{equation}
where $\gamma$ is the stability constant for the standard continuous DPG formulation.
The first inequality follows as we plug in the definition for $a$ and pick
$\bfw=\bfu$. The second equality is trivial, while the next one follows by definition of the optimal test
functions given through the trial-to-test operator $T$. The finally inequality
springs from the fact that
$\sup_{\bfv}\frac{|b(\bfu,\bfv)|}{||\bfv||}\geq\gamma||\bfu||$ and
$||T\bfu||_V=||R_V^{-1}B\bfu||_V=||B\bfu||_{V'}\geq\gamma||u||$.

@@

\begin{figure}[p]
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/StokesCylinder/umag6_NC0.png}
\caption{Nonconservative on initial mesh with $r=0.6$}
\label{fig:stokesCylinder6NC0}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/StokesCylinder/umag6_C0.png}
\caption{Conservative on initial mesh with $r=0.6$}
\label{fig:stokesCylinder6C0}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/StokesCylinder/umag6_NC6.png}
\caption{Nonconservative after 6 refinements with $r=0.6$}
\label{fig:stokesCylinder6NC6}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/StokesCylinder/umag6_C6.png}
\caption{Conservative after 6 refinements with $r=0.6$}
\label{fig:stokesCylinder6C6}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/StokesCylinder/umag9_NC1.png}
\caption{Nonconservative after 1 refinement with $r=0.9$}
\label{fig:stokesCylinder9NC1}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/StokesCylinder/umag9_C1.png}
\caption{Conservative after 1 refinement with $r=0.9$}
\label{fig:stokesCylinder9C1}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/StokesCylinder/umag9_NC6.png}
\caption{Nonconservative after 6 refinements with $r=0.9$}
\label{fig:stokesCylinder9NC6}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/StokesCylinder/umag9_C6.png}
\caption{Conservative after 6 refinements with $r=0.9$}
\label{fig:stokesCylinder9C6}
\end{subfigure}
\caption{Stokes flow around a cylinder - velocity magnitude}
\label{fig:stokesCylinder}
\end{figure}
